Backpropagating Gravitational wave events

### 2022-04-14 src/ms.tex
Update first paragraph

As gravitational-wave (GW) detectors sensitivity improve, the rapid increase of GW detectors shifts out 
\kw{think about the first sentence.}

A very common way to study the origin of detected GW events is through forward modelling of GW progenitor.
Forward modelling of a binary system start with a set of initial binary parameters,
then evolve it according to the physics of interest until some stopping criteria is met.
This usually mean either a merger event or the binary system stays stable for a Hubble time.

@@

    $\alpha$ & Common envelope efficiency & $[0.1,10]$\\
    $f_{\rm acc}$ & Fraction of accretion during stable mass transfer & $[0,1]$\\
    $q_{\rm crit,3}$ & & $[0.1,10]$\\
    $\sigma$ & & $[10,300]\ {\rm km/h}$\\

>>>>

As the rate of detection of gravitational-wave (GW) increase with the sensitivity of the GW detector network \kw{},
understanding astrophysical processes related to progenitors of GW events through analyzing a population of GW events has become more popular \kw{cite}.
A very common way to study the origin of detected GW events is through population synthesis simulation \kw{cite},
which evolves a population of binaries to form a population of GW events.
Forward modelling of a population of GW events start with sampling a set of initial binary parameters from some distributions related to the progenitor population,
such as the initial mass function or star-formation history,
then evolve each individual members according to the physics of interest until some stopping criteria is met.
This usually mean either a merger event or the binary system stays stable for a Hubble time.
After this, one can collect all the GW emitting GW events in the synthetic population and compare to the observed population.

@@

    $\alpha$ & Common envelope efficiency & $[0.1,10]$\\
    $f_{\rm acc}$ & Fraction of accretion during stable mass transfer & $[0,1]$\\
    $q_{\rm crit,3}$ & \kw{Katie fill in} & $[0.1,10]$\\
    $\sigma$ & \kw{Katie fill in}& $[10,300]\ {\rm km/h}$\\
